\documentclass[dvips,11pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{setspace}
\usepackage[total={7in, 9.5in}]{geometry}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{times}

\begin{document}
%=========================title===================================================
\centerline{\it \small CURRICULUM VITAE}
\vspace{2mm}
\centerline{\Large Ching Kai Douglas Wu}  
\centerline{ Louise and James Robert Moffett Molecular Biology Building}
\centerline{2500 Speedway Austin, Room 314 , Austin, TX 78705} 
\centerline{wckdouglas.github.io}
\centerline{\texttt{+}1 (310) 658-1540}
\centerline{wckdouglas@utexas.edu}
\vspace{.5mm}

%Education========================================================================
\noindent{\large \bf EDUCATION} \vspace{-2mm}
\\\noindent \line(1,0){500}\\
\noindent \centerline{\bf The University of Texas at Austin (UT Austin) \hfill Austin, TX}
\noindent \centerline{\textit{\textbf{PhD student (GPA of 3.78), Institute of Cellular \& Molecular Biology \hfill Fall 2013-present}}}
\vspace{-6mm}
\begin{spacing}{0.2}
\begin{itemize} \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item Joint advisors: Dr. Alan M. Lambowitz
	\end{itemize}
\end{spacing} 

\bigskip
\noindent \centerline{\bf University of Illinois at Urbana Champaign (UIUC) \hfill Urbana, IL}
\noindent \centerline{{\textit{\textbf{B.S. (GPA of 3.67), Biochemistry \hfill Fall 2009-Spring2013}}}}
%\begin{spacing}{0.4}
\vspace{-6mm}
\begin{itemize} \itemsep 1pt \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item Biochemistry High Distinction Award
	\end{itemize}
%\end{spacing}
\vspace{-2mm}
\bigskip

%skills========================================================================================
\noindent{\bf \large SKILLS} \vspace{-2mm}
\\\noindent
\vspace{-7mm}
\line(1,0){500}\\

\begin{itemize} \itemsep 1pt \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item Scripting/Programming Languages: {\it Python, R, Bash, MySQL, Matlab, Octave, C++/C}, \LaTeX
	\item Version control: Git
	\item Working knowledge of High Performance Computing: SGE Batch Environment (TACC lonestar), SLURM (TACC stampede)
	\item Working knowledge of High throughput Computing/ Grid computing: HTcondor
	\item Working knowledge of machine learning approaches
\end{itemize}



%RESEARCH EXPERIENCE================================================================
\noindent{\bf \large RESEARCH EXPERIENCE} \vspace{-2mm}
\\\noindent \line(1,0){500}\\
\vspace{-5mm}
%start here========================================

%============rotation 3===============
\noindent \centerline{\bf Prof. Alan Lambowitz's Lab \hfill	Austin, TX}
\noindent \centerline{\textit{\textbf{Institute of Cellular and molecular Biology \hfill Winter 2013-present}}}
\noindent{\bf The University of Texas at Austin}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Perform RNA-seq analysis for exosomal RNA-seq and plasma RNA-seq data
	\item Apply mathematical models on RNA-seq data
	\item Machine learning predictions of RNA modifications
	\item Submitted and prepared 3 manuscripts.
\end{itemize}

%==============Ning Wang's lab===================
\noindent \centerline{\bf Prof. Ning Wang's lab \hfill Urbana, IL}
\noindent \centerline{\bf{\textit{Department of Mechanical Engineering \hfill Spring 2010-Spring 2013} }}
\noindent{\bf University of Illinois at Urbana Champaign}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Studied force-induced biochemical changes in embryonic stem cells
	\item Examined the stress-induce disruption of cajal body using CFP-SMN, YFP-Coilin Hela cells
	\item Worked on 3D-culturing melanoma B16F1 cells, tumorigenic cells, Embryonic stem cells in fibrin matrix 
	\item Co-authored 4 publications
\end{itemize}

%==============Waye's lab================
\noindent\centerline{\bf Prof. Mary Waye's Lab \hfill	Hong Kong}
\noindent\centerline{\textbf{\textit{Department of Biochemistry \hfill Summer 2010}}}
\noindent{\bf Chinese University of Hong Kong}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Investigated KIAA0319 gene on suicide and musically perfect pitch using human DNA extracted from saliva as experimental subject 
	\item Wrote a review on miRNA
\end{itemize}
\newpage

%publication========================================================================================
\bigskip 
\noindent{\bf \large PUBLICATION} \vspace{-1.5mm}
\noindent\\
\vspace{-6mm}
\line(1,0){500}\\
\begin{itemize}
	\setlength{\itemsep}{2pt}
	\item Laura R. Geuss, {\bf Douglas C. Wu}, Divya Ramamoorthy, Corinne D. Alford, Laura J. Suggs. Paramagnetic Beads and Magnetically Mediated Strain Enhance Cardiomyogenesis in Mouse Embryoid Bodies. {\it  PLoS ONE}. Vol. 9, no. 12
	\item Youhua Tan, Arash Tajik, Junwei Chen, Qiong Jia, Farhan Chowdhury, Lili Wang, Junjian Chen, Shuang Zhang, Ying Hong, Haiying Yi, {\bf Douglas C. Wu}, Yuejin Zhang, Fuxiang Wei, Yeh-Chuin Poh, Jihye Seong, Rishi Singh, Li-Jung Lin, Sultan Doganay, Yong Li, Haibo Jia, Taekjip Ha, Yingxiao Wang, Bo Huang, Ning Wang. Matrix softness regulates plasticity of tumour-repopulating cells via H3K9 demethylation and Sox2 expression. {\it Nature Communication}. Vol. 5, no. 4691
 	 \item Yeh-Chuin Poh, Junwei Chen, Ying Hong, Haiying Yi, Shuang Zhang, Junjian Chen, {\bf Douglas C. Wu}, Lili Wang, Qiong Jia, Rishi Singh, Wenting Yao, Youhua Tan, Arash Tajik, Tetsuya S. Tanaka, Ning Wang. Generation of organized mouse germ layers from single embryonic stem cell. {\it Nature Communication}. Vol. 5, no. 4000
	\item Yeh-Chuin Poh, Sergey P. Shevtsov, Farhan Chowdhury, { \bf Douglas C. Wu}, Sungsoo Na, Miroslav Dundr, Ning Wang (2012). Dynamic force-induced direct dissociation of protein complexes in a nuclear body in living cells. {\it Nature Communication}. Vol. 3, no. 866
	\item Yuhei Uda, Yeh-Chuin Poh, Farhan Chowdhury, { \bf Douglas C. Wu}, Tetsuya S. Tanaka, Masaaki Sato, and Ning Wang (2011). Force via integrins but not E-cadherin decreases Oct3/4 expression in embryonic stem cells. {\it Biochemical and Biophysical Research Communications}. Vol. 415, no. 2, pp. 396-400. 
	\item {\bf Douglas Wu} and Mary Waye (2011). The relationship between MicroRNA and Tumor Suppressors, {\it Tumor Suppressors}, eds Susan D. Nguyen (Nova Science Publishers, New York), pp. 175-188. 
\end{itemize}

%Manuscript========================================================================================
\bigskip 
\noindent{\bf \large MANUSCRIPT} \vspace{-1.5mm}
\\\noindent
\line(1,0){500}\\
 \vspace{-6mm}
\begin{itemize} 
	\setlength{\itemsep}{0pt}
				\item Yidan Qin, Jun Yao, {\bf Douglas C. Wu}, Ryan M. Nottingham, Sabine Mohr, Scott Hunicke-Smith and Alan M. Lambowitz. Profiling of circulating RNAs in human plasma by using thermostable group II intron reverse transcriptase template switching. {\it RNA} (In press).
				\item Ryan M. Nottingham$^*$, {\bf Douglas C. Wu$^*$} , Yidan Qin, Jun Yao, Scott Hunicke-Smith, and Alan M. Lambowitz. RNA-Seq of human reference RNA samples using a thermostable group II intron reverse transcriptase.(In preparation) ($^*$co-first author)
				\item {\bf Douglas C. Wu}, Alfread Lentzsch, Jun Yao, Ryan M. Nottingham, Yidan Qin, Claus O. Wilke, and Alan M. Lambowitz. TGIRT-HAMR: Thermostable Group II Intron Reverse Transcriptase High Throughput Annotation of Modified Ribonucleotides. (In preparation)
\end{itemize}




\end{document}