\documentclass[dvips,11pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{setspace}
\usepackage[total={7.5in, 10in}]{geometry}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{times}
\voffset = 0pt
\headheight = 5pt

\begin{document}
%=========================title===================================================
\centerline{\it \small CURRICULUM VITAE}
\vspace{2mm}
\centerline{\Large Ching Kai Douglas Wu}  
\centerline{ Louise and James Robert Moffett Molecular Biology Building}
\centerline{2500 Speedway Austin, Room 314 , Austin, TX 78705} 
\centerline{wckdouglas.github.io}
\centerline{\texttt{+}1 (310) 658-1540}
\centerline{wckdouglas@utexas.edu}
\vspace{.5mm}

%Education========================================================================
\noindent{\large \bf EDUCATION} \vspace{-2.5mm}
\\\noindent \line(1,0){540}\\
\noindent \centerline{\bf The University of Texas at Austin (UT Austin) \hfill Austin, TX}
\noindent \centerline{\textit{\textbf{PhD student, (GPA of 3.81), Institute of Cellular \& Molecular Biology \hfill Fall 2013-present}}} 
\vspace{-7mm}
\begin{spacing}{0.1}
\begin{itemize} \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item Joint advisors: Dr. Alan M. Lambowitz and Dr. Claus O. Wilke 
	\end{itemize}
\end{spacing} 
\vspace{1mm}
\noindent \centerline{\bf University of Illinois at Urbana Champaign (UIUC) \hfill Urbana, IL}
\noindent \centerline{{\textit{\textbf{B.S. (GPA of 3.67), Biochemistry \hfill Fall 2009-Spring2013}}}}
\begin{spacing}{0.2}
\vspace{-2.5mm}
\begin{itemize} \itemsep 1pt \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item Biochemistry High Distinction Award
	\item Dean List (Fall 2010, Spring 2011)
	\item Member of Alpha Lambda Delta Honor Society (Since 2009)
	\end{itemize}
\end{spacing}
\vspace{+2mm}

%RESEARCH EXPERIENCE================================================================
\noindent{\bf \large RESEARCH EXPERIENCE} \vspace{-2mm}
\\\noindent \line(1,0){540}\\
\vspace{-5mm}
%start here========================================

%============rotation 3===============
\noindent \centerline{\bf Prof. Alan Lambowitz's Lab \hfill	Austin, TX}
\noindent \centerline{\textit{\textbf{Institute of Cellular and molecular Biology \hfill Winter 2013-present}}}
\noindent{\bf The University of Texas at Austin}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Whole cell RNA-seq library
	\item RNA-seq analysis for exosomal RNA-seq and plasma RNA-seq data
	\item Applying mathematical models on RNA-seq data
	\item Statistical learning predictions of RNA modifications
\end{itemize}

%==============rotation 2==============
\noindent \centerline{\bf Prof. Claus Wilke's Lab \hfill	Austin, TX}
\noindent \centerline{\textit {\textbf{Institute of Cellular and molecular Biology \hfill Winter 2013-present}}}
\noindent{\bf The University of Texas at Austin}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Bioinformatics: RNA-seq analysis on plasma RNA library
\end{itemize}

%==============rotation 1=============
\noindent \centerline{\bf Prof. Laura Sugg's Lab \hfill	Austin, TX}
\noindent \centerline{\textbf{\textit{Department of Biomedical Engineering \hfill Fall 2013}}}
\noindent{\bf University of Texas at Austin}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Computer simulation for quantifying magnetic-induced force that directs embryoid bodies into mesodermal lineages
\end{itemize}

%==============Ning Wang's lab===================
\noindent \centerline{\bf Prof. Ning Wang's lab \hfill Urbana, IL}
\noindent \centerline{\bf{\textit{Department of Mechanical Engineering \hfill Spring 2010 - Spring 2013} }}
\noindent{\bf University of Illinois at Urbana Champaign}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Study force-induced biochemical changes in embryonic stem cells
	\item Examine the stress-induce disruption of cajal body using CFP-SMN, YFP-Coilin Hela cells
	\item 3D-culturing melanoma B16F1 cells, tumorigenic cells, Embryonic stem cells in fibrin matrix 
\end{itemize}

%==============Waye's lab================
\noindent\centerline{\bf Prof. Mary Waye's Lab \hfill	Hong Kong}
\noindent\centerline{\textbf{\textit{Department of Biochemistry \hfill Summer 2010}}}
\noindent{\bf Chinese University of Hong Kong}
\vspace{-2mm}
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
	\setlength{\itemsep}{0pt}
	\item Investigate KIAA0319 gene on suicide and musically perfect pitch using human DNA extracted from saliva as experimental subject 
\end{itemize}

%publication========================================================================================
\bigskip 
\newpage
\noindent{\bf \large PUBLICATION} \vspace{-1.5mm}
\noindent\\
\vspace{-6mm}
\line(1,0){540}\\
\begin{itemize}
	\setlength{\itemsep}{2pt}
	\item Ryan M. Nottingham$^*$, {\bf Douglas C. Wu$^*$} , Yidan Qin, Jun Yao, Scott Hunicke-Smith, and Alan M. Lambowitz. RNA-Seq of human reference RNA samples using a thermostable group II intron reverse transcriptase. {\it RNA}. Vol. 22, no. 4, pp. 597-613. ($^*$Contributed equally)
	\item Yidan Qin, Jun Yao, {\bf Douglas C. Wu}, Ryan M. Nottingham, Sabine Mohr, Scott Hunicke-Smith and Alan M. Lambowitz (2015). Profiling of circulating RNAs in human plasma by using thermostable group II intron reverse transcriptase template switching. {\it RNA}. Vol. 22, no. 1, pp. 111-128.
	\item Laura R. Geuss, {\bf Douglas C. Wu}, Divya Ramamoorthy, Corinne D. Alford, Laura J. Suggs (2014). Paramagnetic Beads and Magnetically Mediated Strain Enhance Cardiomyogenesis in Mouse Embryoid Bodies. {\it  PLoS ONE}. Vol. 9, no. 12.
	\item Youhua Tan, Arash Tajik, Junwei Chen, Qiong Jia, Farhan Chowdhury, Lili Wang, Junjian Chen, Shuang Zhang, Ying Hong, Haiying Yi, {\bf Douglas C. Wu}, Yuejin Zhang, Fuxiang Wei, Yeh-Chuin Poh, Jihye Seong, Rishi Singh, Li-Jung Lin, Sultan Doganay, Yong Li, Haibo Jia, Taekjip Ha, Yingxiao Wang, Bo Huang, Ning Wang (2014). Matrix softness regulates plasticity of tumour-repopulating cells via H3K9 demethylation and Sox2 expression. {\it Nature Communication}. Vol. 5, no. 4691.
	\item Yeh-Chuin Poh, Junwei Chen, Ying Hong, Haiying Yi, Shuang Zhang, Junjian Chen, {\bf Douglas C. Wu}, Lili Wang, Qiong Jia, Rishi Singh, Wenting Yao, Youhua Tan, Arash Tajik, Tetsuya S. Tanaka, Ning Wang (2014). Generation of organized mouse germ layers from single embryonic stem cell. {\it Nature Communication}. Vol. 5, no. 4000.
	\item Yeh-Chuin Poh, Sergey P. Shevtsov, Farhan Chowdhury, { \bf Douglas C. Wu}, Sungsoo Na, Miroslav Dundr, Ning Wang (2012). Dynamic force-induced direct dissociation of protein complexes in a nuclear body in living cells. {\it Nature Communication}. Vol. 3, no. 866.
	\item Yuhei Uda, Yeh-Chuin Poh, Farhan Chowdhury, { \bf Douglas C. Wu}, Tetsuya S. Tanaka, Masaaki Sato, and Ning Wang (2011). Force via integrins but not E-cadherin decreases Oct3/4 expression in embryonic stem cells. {\it Biochemical and Biophysical Research Communications}. Vol. 415, no. 2, pp. 396-400. 
	\item {\bf Douglas Wu} and Mary Waye (2011). The relationship between MicroRNA and Tumor Suppressors, {\it Tumor Suppressors}, eds Susan D. Nguyen (Nova Science Publishers, New York), pp. 175-188. 
\end{itemize}

%Manuscript========================================================================================
\bigskip 
\noindent{\bf \large MANUSCRIPT} \vspace{-1.5mm}
\\\noindent
\line(1,0){540}\\
 \vspace{-6mm}
\begin{itemize} 
	\setlength{\itemsep}{0pt}
	\item {\bf Douglas C. Wu}, Alfread Lentzsch, Jun Yao, Ryan M. Nottingham, Yidan Qin, Claus O. Wilke, and Alan M. Lambowitz. TGIRT-HAMR: Thermostable Group II Intron Reverse Transcriptase High Throughput Annotation of Modified Ribonucleotides. (In preparation)
\end{itemize}



%skills========================================================================================
\noindent{\bf \large SKILLS} \vspace{-2mm}
\\\noindent
\vspace{-7mm}
\line(1,0){540}\\

\begin{itemize} \itemsep 1pt \parskip 0pt \parsep 0pt
	\setlength{\itemsep}{0pt}
	\item	Languages: Fluent in writing and speaking Mandarin Chinese, Cantonese Chinese
	\item	Programming Languages: {\it Python, R, Bash, Matlab, Octave}, \LaTeX, {\it C++/C},  {\it MySQL}, IGV scripts (Ordered by proficiency)
	\item Working knowledge of High Performance Computing: SGE Batch Environment (TACC lonestar), SLURM (TACC stampede, lonestar 5)
	\item Working knowledge of High throughput Computing/ Grid computing: HTcondor
	\item Working knowledge of machine learning
\end{itemize}

%invited talk========================================================================================
\noindent{\bf \large INVITED TALK} \vspace{-1.5mm}
\\\noindent
\line(1,0){540}\\
\vspace{-6mm}
\begin{itemize} 
	\setlength{\itemsep}{0pt}
	\item High-throughput RNA sequencing with Thermostable Group II Intron Reverse Transcriptase \newline
		{\bf Molecular Bioscience retreat} \newline
		The University of Texas at Austin, Austin, TX. Mar 5, 2016
	\item Next generation sequencing of circulating RNA in plasma \newline
		{\bf Byte club meeting} \newline
		The University of Texas at Austin, Austin TX. Feb 19, 2014 
\end{itemize}

%%Activities========================================================================================
%\noindent{\bf \large ACTIVITY} \vspace{-1.5mm}
%\\\noindent
%\line(1,0){540}\\
%\vspace{-6mm}
%\begin{itemize} 
%	\setlength{\itemsep}{1pt}
%	\item Open Science Grid User Summer School (2014) 
%	\item UIUC Undergraduate research symposium (2013) \newline
%\end{itemize}

%%SPORTS & MUSIC ACHIEVEMENTS
%\bigskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap
%\noindent{\bf \large SPORTS \& MUSIC ACHIEVEMENTS} \vspace{-2mm}%Don’t indent this line and make it bold and large
%\\\noindent
%\vspace{-6mm}
%\line(1,0){470}\\
%\begin{spacing}{0.5}
%\begin{itemize}
%	\setlength{\itemsep}{1pt}
%	\item	Member, Hong Kong Swimming Junior Squad (2006-2009)
%	\item	Shatin Methodist College Swimming Gala A Grade Champion (Fall 2007, Fall 2009)
%	\item	Shatin Methodist College Round Estate Run A Grade Champion (Spring 2007, Spring 2008)
%	\item	Inter-School Swimming Competition A Grade 100m Breakstroke Champion (Fall 2007)
%	\item	Bronze medallion, Hong Kong Life Saving Society (Summer 2007)
%	\item	Pass in Grade 8 Piano (Spring 2007)
%	\item	Pass in Grade 8 Theory of Music (Spring 2006)
%\end{itemize}
%\end{spacing}
%
%%EXTRA CURRICULAR ACTIVITIES
%\bigskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap
%\noindent{\bf \large EXTRA CURRICULAR ACTIVITIES} \vspace{-2mm}%Don’t indent this line and make it bold and large
%\\\noindent
%\line(1,0){470}\\
%\vspace{-6mm}
%\begin{spacing}{0.5}
%\begin{itemize}
%	\setlength{\itemsep}{1pt}
%	\item	HKSA Soccer Team Member (Fall 2009-present)
%	\item	Group Leader in Illini Chinese Christian Fellowship (Fall 2011-Fall 2012)
%	\item	Pianist in Champaign Chinese Christian Church (Fall 2011 – Spring 2012)
%	\item	Secretary of Hong Kong Student Association at UIUC (Fall 2010-Spring 2011)
%	\item	Volunteer in Center of Homeless at South Bend, IN (Fall 2010)
%	\item	Chemistry Enrichment Project (Spring 2010)
%	\item	IHelp at Urbana for health reform (Since Fall 2009)
%\end{itemize}
%\end{spacing}



\end{document}
